Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-20 paper.tex
making clear (along the text) the main objective of the paper

In the research published in this paper, the problem of how many units should be printed  when a new book is published is faced using real data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
Usually, the company's expert sales managers analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions); for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
Nevertheless, just carrying out the analysis and forecasting process as a human expert may lead to imprecise predictions, and they may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

@@

As far as we know, no previous attempt can be found in the literature in which 
prediction methods have been applied to estimate the print run. 
However, similar techniques to those proposed in this paper, e.g. 
regression models \cite{Papalexopoulos1990}, 
neural networks \cite{Yoo1999} 
or fuzzy systems \cite{Mastorocostas2001}, 
have been applied to solve sales prediction problems in other industrial sectors.

@@

In this paper, the problem of how many books should be printed when a new book is going to be published is faced using several data-mining and forecasting methods.

@@

As a conclusion, M5P yields the best results overall, obtaining the best accuracy (lowest error) on average, even with acceptable values regarding the training time.
In addition, the Decision Trees obtained with this method have been presented as an excellent decision-aid tool for publishers, since they are accurate and quite easy to understand and apply. They are also able to provide insights on the decisions that have a higher influence on the print-run for these publishers.

>>>>

In the research published in this paper, the problem 
of predicting total sales in order to print the right amount of books
%of how many units should be printed  when a new book is published 
is faced using real data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
Usually, the company's expert sales managers analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions); for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
Nevertheless, just carrying out the analysis and forecasting process as a human expert may lead to imprecise predictions, and they may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

@@

As far as we know, no previous attempt can be found in the literature 
%in which prediction methods have been applied to estimate the print run. 
in which prediction methods have been applied to estimate sales for new launched books.
However, similar techniques to those proposed in this paper, e.g. 
regression models \cite{Papalexopoulos1990}, 
neural networks \cite{Yoo1999} 
or fuzzy systems \cite{Mastorocostas2001}, 
have been applied to solve sales prediction problems in other industrial sectors.

@@

In this paper, the problem of 
predicting total sales in order to print the right amount of books
%how many books should be printed 
when a new book is going to be published is faced using several data-mining and forecasting methods.

@@

As a conclusion, M5P yields the best results overall, obtaining the best accuracy 
(lowest error) on average, even with acceptable values regarding the training time.
In addition, the Decision Trees obtained with this method have been presented 
as an excellent decision-aid tool for publishers, since they are accurate 
and quite easy to understand and apply. 
They are also able to provide insights on the decisions that have a higher influence on the 
expected sales 
%print-run 
for these publishers.
